Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-25 paper/paper.tex
Iterate section 7

However, I believe that rebuilding a Spanner-like system is difficult for
small- to mid-sized companies because there is a lot of hardware involved, for
example all the GPS and atomic clocks. Unless this hardware infrastructure is
available it is hard to reimplement the TrueTime API. Nonetheless,
companies which need a globally-distributed database with all the guarantees
Spanner provides are likely to be almost as big as Google. Hence, such companies
would also have the resources to build a Spanner-like system. An Open-Source
reimplementation would only be possible if every datacenter would provide GPS
and Armageddon time masters on their own.

@@

It would also be interesting to know how failures of the two singletons per
universe, i.e., universemaster and placement driver, would affect Spanner. Since
the universemaster is just a debugging console, most probably a failure in this
component will not affect Spanner at all. This would probably be a totally
different story if the placement driver does not operate correctly. First of all,
there would be no load balancing between zones. Hence, zones could run out of
space if the placement driver is down long enough. Furthermore, updated
replication constraints, would not be propagated since the placement driver is
responsible to move the data if the replication constraints are modified.
Therefore I do not understand why there is no redundancy in placement driver.

>>>>

However, I believe that rebuilding a Spanner-like system is difficult for
small- to mid-sized companies because there is a lot of hardware involved, for
example, all the GPS and atomic clocks. Unless this hardware infrastructure is
available it is hard to reimplement the TrueTime API. Nonetheless,
companies which need a globally-distributed database with all the guarantees
Spanner provides are likely to be almost as big as Google. Hence, such companies
would also have the resources to build a Spanner-like system. An Open-Source
reimplementation would only be possible if every datacenter would provide GPS
and Armageddon time masters on their own.

@@

It would also be interesting to know how failures of the two singletons per
universe, i.e., universemaster and placement driver, would affect Spanner. Since
the universemaster is just a debugging console, most probably a failure in this
component will not affect Spanner at all. This would probably be a totally
different story if the placement driver does not operate correctly. First of all,
there would be no load balancing between zones. Hence, zones could run out of
space if the placement driver is down for an extended period of time. Furthermore,
updated replication constraints, would not be propagated since the placement
driver is responsible for moving the data if the replication constraints are
modified. Therefore, I do not understand why there is no redundancy in placement
drivers.
